---
title: "Network Models"
author: "Shannon Dickson"
date: "`r format(Sys.Date(), '%B %d %Y')`"
output: 
   bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
    code_folding: hide
    theme: paper
---

<style type="text/css">
  
body{ /* Normal  */
  font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 18px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
  font-size: 18px;
}
h3 { /* Header 3 */
  font-size: 18px;
}
code.r{ /* Code block */
  font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 14px;
}
</style>

---

**Purpose:** I perform Mixed Graphical Modelling on the survey data. 

```{r setup, echo = FALSE}
library(knitr)
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)
```

# Introduction and Set-Up

```{r, echo = FALSE}
# Libraries needed:
library(mgm)
library(qgraph)
library(bootnet)
library(devtools)
library(tidyverse)
library(kableExtra)
library(ggthemes)
# Own function/custom theme:
source("functions.R")
source("plot_theme.R")
# Data:
data        <- readRDS("data/input/data_coded.RDS")
f2f_coded   <- readRDS("data/input/f2f_coded.RDS")
mail_coded  <- readRDS("data/input/mail_coded.RDS")
web_coded   <- readRDS("data/input/web_coded.RDS")
tel_coded   <- readRDS("data/input/tel_coded.RDS")
paper_coded <- readRDS("data/input/paper_coded.RDS")
mail_coded  <- rbind(mail_coded, paper_coded)

# Remove attributes:
data[]       <- lapply(data,       function(x) { attributes(x) <- NULL; x })
f2f_coded[]  <- lapply(f2f_coded,  function(x) { attributes(x) <- NULL; x })
mail_coded[] <- lapply(mail_coded, function(x) { attributes(x) <- NULL; x })
web_coded[]  <- lapply(web_coded,  function(x) { attributes(x) <- NULL; x })
tel_coded[]  <- lapply(tel_coded,  function(x) { attributes(x) <- NULL; x })
```

Since `mgm` can only accept categorical variables coded as integer or numerical, I create a code-key to help understand the different levels. 

```{r, echo = FALSE}
# Create a code-key for the variables:
data_key <- data.frame("Variable" = c("Absolute Relative Bias",
                                      "Nonresponse Rate",
                                      "Year",
                                      "Mode",
                                      "Question Type",
                                      "Reminder",
                                      "Topic",
                                      "Population",
                                      "Saliency",
                                      "Incentives",
                                      "Sponsorship"),
                       
                       "Key"      = c("Numerical",
                                      "Numerical",
                                      "N/A",
                                      "0 = Paper;       1 = F2F;        2 = Mail;   3 = Telephone; 4 = Web",
                                      "0 = Demographic; 1 = Observable; 2 = Unobservable",
                                      "0 = No;          1 = Yes;        2 = Undetermined", 
                                      "0 = Other;       1 = Health",
                                      "0 = No;          1 = Yes",
                                      "0 = No;          1 = Yes",
                                      "0 = No;          1 = Yes",
                                      "0 = No;          1 = Yes"
                                      ))
# Display the key in a nice table:
data_key %>% 
  kbl(caption = "Information on how variables are coded") %>% 
  kable_paper(bootstrap_options = "striped", full_width = TRUE) %>% 
  column_spec(1, bold = TRUE) %>% 
  row_spec(0,    bold = TRUE)
```

# Missing data 

`mgm` cannot handle missingness, so it is useful to get an overview of missingness in the data. 

```{r, echo = FALSE}
# Take a look at missingness:
data %>%
  # Select all columns in the dataset
  select(everything()) %>%
  # Calculate the sum of missing values in each column
  summarise_all(funs(sum(is.na(.)))) %>% 
  # Reshape the data to long format
  pivot_longer(cols = ID:special_population, names_to = "Variable", values_to = "Missing observations (N)") %>% 
  # Create a table object with a caption
  kbl(caption = "Missingness in the data") %>% 
  # Format the table with bootstrap styling
  kable_paper(bootstrap_options = c("striped", "responsive"),
              full_width        = FALSE) %>% 
  # Set the first column (variable names) to bold text
  column_spec(1, bold = TRUE) %>% 
    # Set the first row (column headers) to bold text
  row_spec(0,    bold = TRUE)
```

Visualising the missingness is also informative, we will do this for the entire data set and the mode specific dataset. 

```{r, echo = FALSE}
# Select the relevant variables from each data subset. 
b <- f2f_coded   %>% select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)
c <- mail_coded  %>% select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)
d <- web_coded   %>% select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype) 
e <- tel_coded   %>% select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype) 
f <- paper_coded %>% select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype) 

# Using the plotting function from mice, ;ook at the missingness:
ggmice::plot_pattern(data, rotate = TRUE, square = TRUE)
ggmice::plot_pattern(b, rotate = TRUE, square = TRUE)
ggmice::plot_pattern(c, rotate = TRUE, square = TRUE)
ggmice::plot_pattern(d, rotate = TRUE, square = TRUE)
ggmice::plot_pattern(e, rotate = TRUE, square = TRUE)
ggmice::plot_pattern(f, rotate = TRUE, square = TRUE)
```

# Selecting the network data:

```{r, echo = FALSE}
# Select the variables that we want to include in the network models:
data_net  <- data        %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype, Mode)

f2f_net   <- f2f_coded   %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)

mail_net  <- mail_coded  %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)

web_net   <- web_coded   %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)

tel_net   <- tel_coded   %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)

paper_net <- paper_coded %>%   select(AbsRelbias, MN, Year, Saliency, Incentivised, Reminder, Sponsorship, Topic_Health, special_population, Qtype)

# Combine mail and paper surveys, because there are too few paper surveys:
mail_net <- rbind(mail_net, paper_net)
rm(paper_net)

# Change the colnames so they are more visually appealing in the network graphs:
colnames(data_net) <- paste0("N", rep(1:11))
colnames(f2f_net)  <- paste0("N", rep(1:10))
colnames(web_net)  <- paste0("N", rep(1:10))
colnames(tel_net)  <- paste0("N", rep(1:10))
colnames(mail_net) <- paste0("N", rep(1:10))
```

```{r, echo = FALSE}
# Check for missing and infinite values, and remove them:
is.na(data_net) <- sapply(data_net, is.infinite)
is.na(f2f_net)  <- sapply(f2f_net,  is.infinite)
is.na(mail_net) <- sapply(mail_net, is.infinite)
is.na(web_net)  <- sapply(web_net,  is.infinite)
is.na(tel_net)  <- sapply(tel_net,  is.infinite)

data_net <- na.omit(data_net)
f2f_net  <- na.omit(f2f_net)
mail_net <- na.omit(mail_net)
web_net  <- na.omit(web_net)
tel_net  <- na.omit(tel_net)
```

```{r, echo = FALSE, results = 'hide'}
# mgm needs to know what type of distribution each variable/node belongs to, and how many levels it has:
# below we create lists for the variable type, level, and name, which we will attach to the data list.
# type is "Gaussian" or "Categorical"; "g" or "c":

# For the overall network:
type_all   <- c("g", "g", "g", "c", "c", "c", "c", "c", "c", "c", "c")
levels_all <- c(1,   1,   1,   2,   2,   2,   2,   2  , 2,   3,   5)
names_all  <- c(
                "Nonresponse bias",
                "Nonresponse rate",
                "Year",
                "Salient topic",
                "Incentives given",
                "Reminders given",
                "Sponsored survey",
                "Health/Other topic",
                "Special population",
                "Question type",
                "Survey mode"
                )

groups_all <- c(rep(c("Outcome"), 2), rep(c("Survey Design Characteristics"), 9))

# For the mode-specific networks:
type   <- c("g", "g", "g", "c", "c", "c", "c", "c", "c", "c")
levels <- c(1,   1,   1,   2,   2,   2,   2,   2,   2,   3)
names  <- c(
            "Nonresponse bias",
            "Nonresponse rate",
            "Year",
            "Salient topic",
            "Incentives given",
            "Reminders given",
            "Sponsored survey",
            "Health/Other topic",
            "Special population",
            "Question type"
            )

groups <- c(rep(c("Survey Outcomes"), 2), rep(c("Survey Design Characteristics"), 8))


# Combine this information with the dataframes:
data_net_list <- list(data = data_net, type = type_all, level = levels_all, colnames = paste0("N", rep(1:11)),  names = names_all, groups = groups_all)

f2f_net_list  <- list(data = f2f_net,  type = type,     level = levels,     colnames = paste0("N", rep(1:10)),  names = names, groups = groups)

web_net_list  <- list(data = web_net,  type = type,     level = levels,     colnames = paste0("N", rep(1:10)),  names = names, groups = groups)

mail_net_list <- list(data = mail_net, type = type,     level = levels,     colnames = paste0("N", rep(1:10)), names = names, groups = groups)

tel_net_list  <- list(data = tel_net,  type = type,     level = levels,     colnames = paste0("N", rep(1:10)),  names = names, groups = groups)

# Quick check that everything is correct:
length(type_all)
length(levels_all)
length(data_net)
length(names_all)

length(f2f_net)
length(levels)
length(type)
length(names)
```

# Network Modelling

I will estimate an overall network *and* a network for each mode, because we expect our outcomes (nonresponse rates and nonresponse bias) to behave differently over modes. There are two main ways to do this:

1. Estimate an overall network to check that mode matters, then split the data by mode and estimate a network for each. Possibly conduct a NCT.
2. Estimate a moderated MGM, where mode is selected as the moderator and 3-way interactions are estimated between mode and all other variables. 

A simulation study suggested that moderated MGM perform better, so I will try this first. It will be important to estimate bootstrapped stability of the network parameters for both methods and make a comparison.  

## Moderated MGM

Estimation is the same, but I specify the moderating variable `Mode` which is variable 11. 

```{r, eval=FALSE, echo = FALSE}
# Set a seed for reproducibility:
set.seed(123)
# Estimate the moderated MGM:
mgm_mod <- mgm(data       = as.matrix(data_net_list$data), 
               type       = data_net_list$type,
               level      = data_net_list$levels,
               moderators = 1,
               lambdaSel  = 'EBIC', 
               lambdaGam  = 0.25,
               ruleReg    = "OR",
               binarySign = TRUE,
               scale      = TRUE, 
               pbar       = FALSE)

# The condition function from mgm holds the moderator variable and levels constant,
# and estimates a network based on the specified level:

# Condition 0 estimates a network where the moderator is Mode == Paper:
cond0 <- condition(object = mgm_mod, 
                   values = list('1' = 0))
# Condition 1 estimates a network where the moderator is Mode == F2F:
cond1 <- condition(object = mgm_mod, 
                   values = list('1' = 1))
# Condition 2 estimates a network where the moderator is Mode == Mail:
cond2 <- condition(object = mgm_mod, 
                   values = list('1' = 2))
# Condition 3 estimates a network where the moderator is Mode == Telephone:
cond3 <- condition(object = mgm_mod, 
                   values = list('1' = 3))
# Condition 4 estimates a network where the moderator is Mode == Web:
cond4 <- condition(object = mgm_mod, 
                   values = list('1' = 4))

# Create a list of the conditions, we will use for plotting:
conditions <- list(cond0, cond1, cond2, cond3, cond4)

# Set the max value to the maximum value within each network weighted adjacency matrix:
max_val <- max(max(conditions[[1]]$pairwise$wadj),
               max(conditions[[2]]$pairwise$wadj),
               max(conditions[[3]]$pairwise$wadj),
               max(conditions[[4]]$pairwise$wadj),
               max(conditions[[5]]$pairwise$wadj))

#L <- averageLayout(conditions[[i]]$pairwise$wadj)

# Overall plot
qgraph(input          = mgm_mod$pairwise$wadj,
       layout         = "circle",
       edge.color     = mgm_mod$pairwise$edgecolor, 
       legend.cex     = 0.5,
       vsize          = 7,
       esize          = 10,
       font           = 4,
       filetype       = "png",
       filename       = "img/moderated_networks/mgm_mod",
       bg             = "transparent")

# Partition a plot space:                                    
#par(mfrow=c(3, 2))

# Iterate over the conditions with qgraph:
for(i in 1:5) qgraph(input      = conditions[[i]]$pairwise$wadj,
                     layout     = "circle",
                     edge.color = c("#273B5B", "#E48F1B", "#A9A9A9"),
                     labels     = TRUE, 
                     label.font = 4, 
                     #nodeNames  = data_net_list$names,
                     maximum    = max_val,
                     legend.cex = 0.7,
                     vsize      = 7,
                     esize      = 10,
                     font       = 4,
                     #title      = paste0("Mode = ", c("Paper", "F2F", "Mail", "Telephone", "Web")[i]),
                     filetype   = "png",
                     filename   = paste0("img/moderated_networks/mgm_mod_", c("paper", "f2f", "mail", "telephone", "web")[i]),
                     bg         = "transparent")
```



## Split modes

```{r, echo = FALSE}
# Set a seed for reproducibility:
set.seed(123)

# Estimate the network for all modes together:
mgm_all <- mgm(# Convert the data to matrix format
               data       = as.matrix(data_net_list$data), 
               # Specify the type of data 
               type       = data_net_list$type,
               # Specify the levels of the variables
               level      = data_net_list$levels,
               # Order of interactions = 2 for pairwise
               k          = 2,
               # Model selection using EBIC
               lambdaSel  = 'EBIC', 
               # Tuning parameter for model complexity
               lambdaGam  = 0.25,
               # Return edges when either nodewise estimate is nonzero
               ruleReg    = "OR",
               # Add the sign/color for binary variables
               binarySign = TRUE,
               # Scale/standardize parameters
               scale      = TRUE)

# Estimate the network for face-to-face surveys:
mgm_f2f <- mgm(data       = as.matrix(f2f_net_list$data), 
               type       = f2f_net_list$type,
               level      = f2f_net_list$levels,
               k          = 2,
               lambdaSel  = 'EBIC', 
               lambdaGam  = 0.25,
               ruleReg    = "OR",
               binarySign = TRUE,
               scale      = TRUE)

# Estimate the network for web surveys:
mgm_web <- mgm(data       = as.matrix(web_net_list$data), 
               type       = web_net_list$type,
               level      = web_net_list$levels,
               k          = 2,
               lambdaSel  = 'EBIC', 
               lambdaGam  = 0.25,
               ruleReg    = "OR",
               binarySign = TRUE,
               scale      = TRUE)

# Estimate the network for mail surveys:
mgm_mail <- mgm(data      = as.matrix(mail_net_list$data), 
               type       = mail_net_list$type,
               level      = mail_net_list$levels,
               k          = 2,
               lambdaSel  = 'EBIC', 
               lambdaGam  = 0.25,
               ruleReg    = "OR",
               binarySign = TRUE,
               scale      = TRUE)

# Estimate the network for telephone surveys:
mgm_tel <- mgm(data       = as.matrix(tel_net_list$data), 
               type       = tel_net_list$type,
               level      = tel_net_list$levels,
               k          = 2,
               lambdaSel  = 'EBIC', 
               lambdaGam  = 0.25,
               ruleReg    = "OR",
               binarySign = TRUE,
               scale      = TRUE)
```

## Predictions

```{r}
# Get the network predictions:
mgm_predict_all <- predict(object   = mgm_all,
                           data     = data_net_list$data, 
                           # normalised number of correct classifications for categorical nodes
                           errorCat = 'nCC',
                           # explained variance (R2) for continuous nodes
                           errorCon = 'R2')

mgm_predict_f2f <- predict(object   = mgm_f2f,
                           data     = f2f_net_list$data, 
                           errorCat = 'nCC',
                           errorCon = 'R2')

mgm_predict_web <- predict(object   = mgm_web,
                           data     = web_net_list$data, 
                           errorCat = 'nCC',
                           errorCon = 'R2')

mgm_predict_mail <- predict(object   = mgm_mail,
                            data     = mail_net_list$data, 
                            errorCat = 'nCC',
                            errorCon = 'R2')

mgm_predict_tel <- predict(object   = mgm_tel,
                           data     = tel_net_list$data, 
                           errorCat = 'nCC',
                           errorCon = 'R2')

# Create a list of all the predictions
predictions_list <- list(mgm_predict_all$errors,
                         mgm_predict_f2f$errors,
                         mgm_predict_web$errors,
                         mgm_predict_mail$errors,
                         mgm_predict_tel$errors)
```

```{r}
# Create a neat list of the errors for all variable types,
# Looping over the continuous and then the categorical errors.

errors_all <- c()
colors_all <- c()

for(i in 1:3)       errors_all[[i]] <- predictions_list[[1]][i,2]
for(i in c(4:11))   errors_all[[i]] <- predictions_list[[1]][i,3]

for(i in 1:3)       colors_all[[i]] <- "#7fc97f"
for(i in c(4:11))   colors_all[[i]] <- c("#fec66b")

errors_f2f <- c()
colors_f2f <- c()

for(i in 1:3)       errors_f2f[[i]] <- predictions_list[[2]][i,2]
for(i in c(4:10))   errors_f2f[[i]] <- predictions_list[[2]][i,3]

for(i in 1:3)       colors_f2f[[i]] <-   "#7fc97f"
for(i in c(4:10))   colors_f2f[[i]] <- c("#fec66b")

errors_mail <- c()
colors_mail <- c()

for(i in 1:3)       errors_mail[[i]] <- predictions_list[[3]][i,2]
for(i in c(4:10))   errors_mail[[i]] <- predictions_list[[3]][i,3]

for(i in 1:3)       colors_mail[[i]] <-   "#7fc97f"
for(i in c(4:10))   colors_mail[[i]] <- c("#fec66b")

errors_web <- c()
colors_web <- c()

for(i in 1:3)       errors_web[[i]] <- predictions_list[[4]][i,2]
for(i in c(4:10))   errors_web[[i]] <- predictions_list[[4]][i,3]
  
for(i in 1:3)       colors_web[[i]] <-   "#7fc97f"
for(i in c(4:10))   colors_web[[i]] <- c("#fec66b")

errors_tel <- c()
colors_tel <- c()

for(i in 1:3)       errors_tel[[i]] <- predictions_list[[5]][i,2]
for(i in c(4:10))   errors_tel[[i]] <- predictions_list[[5]][i,3]

for(i in 1:3)       colors_tel[[i]] <-   "#7fc97f"
for(i in c(4:10))   colors_tel[[i]] <- c("#fec66b")

```

```{r}
# These parameters should be known for the networks:

# the maximum edge weight over the split netwotks
max_val <- max(
               max(mgm_f2f$pairwise$wadj),
               max(mgm_web$pairwise$wadj),
               max(mgm_mail$pairwise$wadj),
               max(mgm_tel$pairwise$wadj))

# the minimum edge weight over the split netwotks
min_val <- min(
               min(mgm_f2f$pairwise$wadj),
               min(mgm_web$pairwise$wadj),
               min(mgm_mail$pairwise$wadj),
               min(mgm_tel$pairwise$wadj))

# a value to cut above/below the edge weight (75th percentile as recommended)
cut_val <- max(
               quantile(mgm_f2f$pairwise$wadj,  .75),
               quantile(mgm_web$pairwise$wadj,  .75),
               quantile(mgm_mail$pairwise$wadj, .75),
               quantile(mgm_tel$pairwise$wadj,  .75))

# Create an average layout for the network models, so it is easier to visually compare them:
L <- averageLayout(mgm_f2f$pairwise$wadj,
                   mgm_tel$pairwise$wadj,
                   mgm_mail$pairwise$wadj,
                   mgm_web$pairwise$wadj,
                   layout = 'spring')

# Change the positive and negative colours in the network to nicer shades of blue and red:
mgm_all$pairwise$edgecolor  <- ifelse(mgm_all$pairwise$edgecolor == "darkgreen", "blue",  mgm_all$pairwise$edgecolor)
mgm_all$pairwise$edgecolor  <- ifelse(mgm_all$pairwise$edgecolor == "red", "#cb4154",     mgm_all$pairwise$edgecolor)

mgm_f2f$pairwise$edgecolor  <- ifelse(mgm_f2f$pairwise$edgecolor == "darkgreen", "blue",  mgm_f2f$pairwise$edgecolor)
mgm_f2f$pairwise$edgecolor  <- ifelse(mgm_f2f$pairwise$edgecolor == "red", "#cb4154",     mgm_f2f$pairwise$edgecolor)

mgm_mail$pairwise$edgecolor <- ifelse(mgm_mail$pairwise$edgecolor == "darkgreen", "blue", mgm_mail$pairwise$edgecolor)
mgm_mail$pairwise$edgecolor <- ifelse(mgm_mail$pairwise$edgecolor == "red", "#cb4154",    mgm_mail$pairwise$edgecolor)

mgm_web$pairwise$edgecolor  <- ifelse(mgm_web$pairwise$edgecolor == "darkgreen", "blue",  mgm_web$pairwise$edgecolor)
mgm_web$pairwise$edgecolor  <- ifelse(mgm_web$pairwise$edgecolor == "red", "#cb4154",     mgm_web$pairwise$edgecolor)

mgm_tel$pairwise$edgecolor  <- ifelse(mgm_tel$pairwise$edgecolor == "darkgreen", "blue",  mgm_tel$pairwise$edgecolor)
mgm_tel$pairwise$edgecolor  <- ifelse(mgm_tel$pairwise$edgecolor == "red", "#cb4154",     mgm_tel$pairwise$edgecolor)
```

```{r, echo = FALSE}
# Plot the networks networks:

# for the network of all modes
qgraph(input       = mgm_all$pairwise$wadj,
       edge.color  = mgm_all$pairwise$edgecolor,
       color       = rep("white", 2),
       # add in the errors and colours
       pie         = errors_all, 
       pieColor    = colors_all,
       # we do not use max and cut in the overall network
       #maximum     = max_val,
       #cut         = cut_val,
       # some plotting parameters
       nodeNames   = data_net_list$names,
       groups      = data_net_list$groups,
       labels      = paste0("N", rep(1:11)),
       legend.cex  = 0.50,
       GLratio     = 1.8,
       legend      = FALSE,
       legend.mode = "style1",
       layout      = "spring",
       vsize       = 7,
       font        = 4,
       filetype    = "png", 
       filename    = "img/split_networks/mgm_all",
       width       = 8,
       height      = 8,
       bg          = "transparent")

# for the network of face-to-face surveys
qgraph(input       = mgm_f2f$pairwise$wadj,
       edge.color  = mgm_f2f$pairwise$edgecolor,
       color       = rep("white", 2),
       pie         = errors_f2f, 
       pieColor    = colors_f2f,
       # we use cut instead of max, so the edges aren't drowned out
       #maximum     = max_val,
       cut         = cut_val,
       nodeNames   = f2f_net_list$names,
       groups      = f2f_net_list$groups,
       labels      = paste0("N", rep(1:10)),
       legend.cex  = 0.50,
       GLratio     = 1.8,
       legend      = FALSE,
       legend.mode = "style1",
       layout      = L,
       vsize       = 7,
       font        = 4,
       filetype    = "png", 
       filename    = "img/split_networks/mgm_f2f",
       width       = 8,
       height      = 8,
       bg          = "transparent")

# for the network of mail surveys
qgraph(input       = mgm_mail$pairwise$wadj,
       edge.color  = mgm_mail$pairwise$edgecolor,
       color       = rep("white", 2),
       pie         = errors_mail, 
       pieColor    = colors_mail,
       #maximum     = max_val,
       cut         = cut_val,
       nodeNames   = mail_net_list$names,
       groups      = mail_net_list$groups,
       labels      = paste0("N", rep(1:10)),
       legend.cex  = 0.50,
       GLratio     = 1.8,
       legend      = FALSE,
       legend.mode = "style1",
       layout      = L,
       vsize       = 7,
       font        = 4,
       groups      = mail_net_list$groups,
       filetype    = "png", 
       filename    = "img/split_networks/mgm_mail",
       width       = 8,
       height      = 8,
       bg          = "transparent")

# for the network of webs surveys
qgraph(input       = mgm_web$pairwise$wadj,
       edge.color  = mgm_web$pairwise$edgecolor,
       color       = rep("white", 2),
       pie         = errors_web, 
       pieColor    = colors_web,
       #maximum     = max_val,
       cut         = cut_val,
       nodeNames   = web_net_list$names,
       groups      = web_net_list$groups,
       labels      = paste0("N", rep(1:10)),
       legend.cex  = 0.50,
       GLratio     = 1.8,
       legend      = FALSE,
       legend.mode = "style1",
       layout      = L,
       vsize       = 7,
       font        = 4,
       filetype    = "png", 
       filename    = "img/split_networks/mgm_web",
       width       = 8,
       height      = 8,
       bg          = "transparent")

# for the network of telephone surveys
qgraph(input       = mgm_tel$pairwise$wadj,
       edge.color  = mgm_tel$pairwise$edgecolor,
       color       = rep("white", 2),
       pie         = errors_tel, 
       pieColor    = colors_tel,
       #maximum     = max_val,
       cut         = cut_val,
       nodeNames   = tel_net_list$names,
       groups      = tel_net_list$groups,
       labels      = paste0("N", rep(1:10)),
       legend.cex  = 0.50,
       GLratio     = 1.8,
       legend      = FALSE, 
       legend.mode = "style1",
       layout      = L,
       vsize       = 7,
       font        = 4,
       filetype    = "png", 
       filename    = "img/split_networks/mgm_telephone",
       width       = 8,
       height      = 8,
       bg          = "transparent")
```

# Pairwise and Nodewise Interactions

Network models have nodewise estimates (one set in each direction of a node pair) and pairwise estimates (average of the nodewise pairs). Below we save this information for the appendix information of the manuscript.  

```{r, echo = FALSE}
# # the maximum edge weight over the split netwotks
overall_pairwise <- data.frame(mgm_all$pairwise$wadj,         row.names = colnames(data_net))
overall_pairwise <- data.frame(mgm_all$pairwise$wadjNodewise, row.names = colnames(data_net))
# Add column names to the data frame:
colnames(overall_pairwise)<-names(data_net)
colnames(overall_pairwise)<-names(data_net)
# Save the dataframes as RDS files:
saveRDS(overall_pairwise, "data/output/overall_pairwise.RDS")
saveRDS(overall_pairwise, "data/output/overall_nodewise.RDS")

# F2F network
f2f_pairwise <- data.frame(mgm_f2f$pairwise$wadj,         row.names = colnames(f2f_net))
f2f_nodewise <- data.frame(mgm_f2f$pairwise$wadjNodewise, row.names = colnames(f2f_net))
# Add column names to the data frame:
colnames(f2f_pairwise) <- names(f2f_net)
colnames(f2f_pairwise) <- names(f2f_net)
# Save the dataframes as RDS files:
saveRDS(f2f_pairwise, "data/output/f2f_pairwise.RDS")
saveRDS(f2f_pairwise, "data/output/f2f_nodewise.RDS")

# Web network
web_pairwise <- data.frame(mgm_web$pairwise$wadj,         row.names = colnames(web_net))
web_pairwise <- data.frame(mgm_web$pairwise$wadjNodewise, row.names = colnames(web_net))
# Add column names to the data frame:
colnames(web_pairwise) <- names(web_net)
colnames(web_pairwise) <- names(web_net)
# Save the dataframes as RDS files:
saveRDS(web_pairwise, "data/output/web_pairwise.RDS")
saveRDS(web_pairwise, "data/output/web_nodewise.RDS")

# Mail network
mail_pairwise <- data.frame(mgm_mail$pairwise$wadj,         row.names = colnames(mail_net))
mail_nodewise <- data.frame(mgm_mail$pairwise$wadjNodewise, row.names = colnames(mail_net))
# Add column names to the data frame:
colnames(mail_pairwise) <- names(mail_net)
colnames(mail_pairwise) <- names(mail_net)
# Save the dataframes as RDS files:
saveRDS(mail_pairwise, "data/output/mail_pairwise.RDS")
saveRDS(mail_pairwise, "data/output/mail_nodewise.RDS")

# Telephone network
tel_pairwise <- data.frame(mgm_tel$pairwise$wadj,         row.names = colnames(tel_net))
tel_pairwise <- data.frame(mgm_tel$pairwise$wadjNodewise, row.names = colnames(tel_net))
# Add column names to the data frame:
colnames(tel_pairwise) <- names(tel_net)
colnames(tel_pairwise) <- names(tel_net)
# Save the dataframes as RDS files:
saveRDS(tel_pairwise, "data/output/tel_pairwise.RDS")
saveRDS(tel_pairwise, "data/output/tel_nodewise.RDS")
```

# Network Centrality

Network centrality measures can be estimated using the `bootnet` package, but as this does not accept `mgm` objects we use the `estimateNetwork` function from `bootnet` which calls to the `mgm` package. 

```{r, eval=F}
set.seed(123)
# Estimate the networks with bootnet:

# for the overall network
overall_net_strength <- bootnet::estimateNetwork(data_net_list$data,
                                                 type =  data_net_list$type,
                                                 level = data_net_list$level,
                                                 rule = "OR",
                                                 binarySign = TRUE,
                                                 default = "mgm")

# for the face-to-face network
f2f_net_strength  <- bootnet::estimateNetwork(f2f_net_list$data, 
                                              type =  f2f_net_list$type,
                                              level = f2f_net_list$level,
                                              default = "mgm")

# for the mail network
mail_net_strength <- bootnet::estimateNetwork(mail_net_list$data, 
                                              type =  mail_net_list$type,
                                              level = mail_net_list$level,
                                              default = "mgm")

# for the web network
web_net_strength  <- bootnet::estimateNetwork(web_net_list$data, 
                                              type =  web_net_list$type,
                                              level = web_net_list$level,
                                              default = "mgm")

# for the telephone network
tel_net_strength  <- bootnet::estimateNetwork(tel_net_list$data, 
                                              type =  tel_net_list$type,
                                              level = tel_net_list$level,
                                              default = "mgm")

# we plot the centrality (strength) for the overal network:
strength_overall <-  centralityPlot(overall_net_strength,
                               scale = "z-scores",
                               include = "Strength") +
                               labs(x = "Standardized z-score", y = "Node", color=NULL) +
                               theme_thesis() +
                               theme(legend.position = "right",
                               legend.direction = "vertical")

# we plot the strength centrality of the stratified networks
all_strength <- centralityPlot(list(
                                    "Face-to-face" = f2f_net_strength,
                                    "Mail" = mail_net_strength,
                                    "Web" = web_net_strength,
                                    "Telephone" = tel_net_strength),
                                     scale = "z-scores",
                                     include = "Strength") +
                                     labs(x = "Standardized z-score", y = "Node", color=NULL) +
                                     scale_colour_thesis() + theme_thesis() +
                                     theme(legend.position = "right",
                                    legend.direction = "vertical") 

# Save strength plots:
ggsave('img/centrality_plots/strength_overall.png',  strength_overall, bg ='transparent', height = 7, width = 5)
ggsave('img/centrality_plots/all_strength.png',  all_strength, bg ='transparent', height = 7, width = 5)
```

# Network Stability

Using the `bootnet` function from the `bootnet` package, we estimate the **Bootstrapped Confidence Intervals** which show the variability in parameter estimates that is to be expected in the data. 

Note that evaluation of this chunk is set to `FALSE`, because it takes somewhere between 12-18 hours depending on your device. I recommend skipping this step and checking the saved output, or reducing the number of bootstraps to 1 in order to check the function works. 

```{r, eval=F}
# I customised my own function, to perform bootstrapping over a list of networks, given some specifications (see "functions.R")
dfs <- list(overall_net_strength, f2f_net_strength, mail_net_strength, web_net_strength, tel_net_strength)
# Run the bootstrap tests for each network
boots_nonparametric <- do_stability(dfs, nB = 1000, nC = 8, which_boot = "NP")
boots_casedropping  <- do_stability(dfs, nB = 1000, nC = 8, which_boot = "CD")
# Save the output
saveRDS(boots_nonparametric, "data/output/boots_nonparametric.RDS")
saveRDS(boots_casedropping,  "data/output/boots_casedropping.RDS")
```

```{r, message=F,warning=F,eval=F}
# read in the bootstrapp results:
boots_nonparametric <- readRDS("data/output/boots_nonparametric.RDS")
boots_casedropping <- readRDS("data/output/boots_casedropping.RDS")

# plot the stability of edge estimates, using my custom function (see "functions.R")
plots_np_edge <- plot_stability(boots_nonparametric, which_boot = "NP", which_plot = "accuracy",   panels = FALSE, labels = TRUE, legend = "none")
# plot the stability of strength estimates, using my custom function (see "functions.R")
plots_cd_stre <- plot_stability(boots_casedropping,  which_boot = "CD", which_plot = "stability",  panels = FALSE, legend = "none")

# Save the images that result from plot_stability
ggsave('img/boot_plots/p_np_accuracy_all.png',     plots_np_edge[[2]][[1]], bg ='transparent', height = 8, width = 4, dpi = 300)
ggsave('img/boot_plots/p_np_accuracy_f2f.png',     plots_np_edge[[2]][[2]], bg ='transparent', height = 8, width = 4, dpi = 300)
ggsave('img/boot_plots/p_np_accuracy_mail.png',    plots_np_edge[[2]][[3]], bg ='transparent', height = 8, width = 4, dpi = 300)
ggsave('img/boot_plots/p_np_accuracy_web.png',     plots_np_edge[[2]][[4]], bg ='transparent', height = 8, width = 4, dpi = 300)
ggsave('img/boot_plots/p_np_accuracy_tel.png',     plots_np_edge[[2]][[5]], bg ='transparent', height = 8, width = 4, dpi = 300)
ggsave('img/boot_plots/p_np_accuracy.png',         plots_np_edge[[6]][[2]], bg ='transparent', height = 16, width = 16, dpi = 300)

ggsave('img/boot_plots/p_cd_stability_all.png',    plots_cd_stre[[5]][[1]],      bg ='transparent', height = 5, width = 10, dpi = 300)
ggsave('img/boot_plots/p_cd_stability_f2f.png',    plots_cd_stre[[5]][[2]],      bg ='transparent', height = 5, width = 10, dpi = 300)
ggsave('img/boot_plots/p_cd_stability_mail.png',   plots_cd_stre[[5]][[3]],      bg ='transparent', height = 5, width = 10, dpi = 300)
ggsave('img/boot_plots/p_cd_stability_web.png',    plots_cd_stre[[5]][[4]],      bg ='transparent', height = 5, width = 10, dpi = 300)
ggsave('img/boot_plots/p_cd_stability_tel.png',    plots_cd_stre[[5]][[5]],      bg ='transparent', height = 5, width = 10, dpi = 300)
ggsave('img/boot_plots/p_cd_stability.png',        plots_cd_stre[[6]],           bg ='transparent', height = 5, width = 10, dpi = 300)
``` 

# Nodewise interactions

I created functions (see `functions.R`) to extract the pairwise interactions of the node levels, merges it into a dataframe instead of an ugly list, and saves it. These dataframes do not include the aggregate estimate for the node, because that information is stored somewhere else in the model object (annoying). A challenge for another day. 

```{r}
# get all the interactions in a list:
overall_ints    <- get_interactions(network = mgm_all,  n_nodes = 11, separate = TRUE)
f2f_ints        <- get_interactions(network = mgm_f2f,  n_nodes = 10, separate = TRUE)
mail_ints       <- get_interactions(network = mgm_mail, n_nodes = 10, separate = TRUE)
web_ints        <- get_interactions(network = mgm_web,  n_nodes = 10, separate = TRUE)
tel_ints        <- get_interactions(network = mgm_tel,  n_nodes = 10, separate = TRUE)

# get all the interactions in a matrix:
df_ints_overall <- merge_ints(interactions = overall_ints, n_nodes=11)
df_ints_f2f     <- merge_ints(interactions = f2f_ints,     n_nodes=10)
df_ints_mail    <- merge_ints(interactions = mail_ints,    n_nodes=10)
df_ints_web     <- merge_ints(interactions = web_ints,     n_nodes=10)
df_ints_tel     <- merge_ints(interactions = tel_ints,     n_nodes=10)

# save the list of dataframes:
saveRDS(df_ints_overall, "data/output/df_ints_overall.RDS")
saveRDS(df_ints_f2f,     "data/output/df_ints_f2f.RDS")
saveRDS(df_ints_mail,    "data/output/df_ints_mail.RDS")
saveRDS(df_ints_web,     "data/output/df_ints_web.RDS")
saveRDS(df_ints_tel,     "data/output/df_ints_tel.RDS")
```
